A robust framework for variable extrusion width concentric toolpath generation

### 2019-07-08 4_method.tex
describe tick placement algorithms

\subsubsection{Processing order}
\hl{How do we process the graph?}
\begin{itemize}
\item walk along polygons and for each vert walk down the graph up to the desired depth
\item process nodes in depth first order
\item process nodes in $R$ sorted order
\end{itemize}

We would require either a mapping from locations or bones to toolpath segments, which we can use to efficiently connect paths together.

Or we process all segments in order of the polygon, but then we need to track which polygons have been processed.

If we don't process both sides of the gMAT at the same time then we should record certain calculations such as the transition locations and maye also the parabola sample points.

\hl{Is there or should there be a specific ordering on the bones connected to a joint?}
A joint can have multiple parents.
We could order the bones cyclically, irrespective of whether they are going `up' or `down'.

>>>>

\subsubsection{Toolpath extraction algorithm}
After the beading strategy has been applied we have a beading associated with each significant node as well as each node with locally optimal $R$.
In order to determine the tick locations of quads which don't contain any such node, we propagate the beading information down.
We therefore sort all quads on their highest $R$-value and process the high $R$ quads first.
The beading information is then passed down along the bones of the quad to lower $R$ nodes if those nodes don't already have a beading associated.

See \cref{alg_beading_propagation}.

\begin{algorithm}
\caption{Beading propagation}
\label{alg_beading_propagation}
\begin{algorithmic}
\State quads.sortOn(getHighestR())
\ForAll{$q \in$ quads}
	\State $v_\text{max} = q$.getHighestR()
	\State beading = retrieveBeading($v_\text{max}$)
	\If {$\neg$ retrieveBeading($v_\text{max}$.next())}
		\State storeBeading($v_\text{max}$.next(), beading)
	\EndIf
	\If {$\neg$ retrieveBeading($v_\text{max}$.prev())}
		\State storeBeading($v_\text{max}$.prev(), beading)
	\EndIf
\EndFor
\end{algorithmic}
\end{algorithm}

We can then process all bones in arbitrary order and generate the ticks along those bones.
See \cref{alg_tick_generation}.

\begin{algorithm}
\caption{Tick generation}
\label{alg_tick_generation}
\lstset{language=C++}
\begin{lstlisting}[frame=single]
Point a = edge->to->p;
Point b = edge->from->p;
Point ab = b - a;

int start_R = edge->to->data.distance_to_boundary; // higher R
int end_R = edge->from->data.distance_to_boundary; // lower R
assert(end_R <= start_R);

int junction_idx;
// compute starting junction_idx for this segment
for (junction_idx = (beading->toolpath_locations.size() - 1) / 2; junction_idx >= 0 && junction_idx < beading->toolpath_locations.size(); junction_idx--)
{
  int bead_R = beading->toolpath_locations[junction_idx];
  if (bead_R <= start_R)
    break; // junction coinciding with start node is used in this function call
}

for (; junction_idx >= 0 && junction_idx < coord_t(beading->toolpath_locations.size()); junction_idx--)
{
  int bead_R = beading->toolpath_locations[junction_idx];
  assert(bead_R > 0);
  if (bead_R < end_R)
    break; // junction coinciding with a node is handled by the next segment

  Point junction(a + ab * (bead_R - start_R) / (end_R - start_R));
  ticks.emplace_back(junction, beading->bead_widths[junction_idx], junction_idx);
}
\end{lstlisting}
\end{algorithm}

We then generate bead segments for each quad by connecting together the ticks of the same index.
If the amount of ticks on both sides of the quad is not the same then this quad is in a transition and we leave one tick unconnected.
